%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Homework 1: Lateral Inhibition} % Title of the assignment

\author{Oliver Rutving s164209} % Author name and email address

\date{Introduction to Cognitive Science 02454 --- \today} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------


\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Exercise 1} % Numbered section
Let $x_1, x_2, x_3$ represent how many deciliters of each product A, B or C should be produced. 
\\
She can sell product A for 60kr per liter, product B for 70kr per liter and product C for 30kr per liter. This gives the objective function $Z=6x_1+7x_2+3x_3$. 
The objective function says that for every dl of product A sold she will profit 6kr. If she sells 2dl of each product, she will earn $Z=6*2+7*2+3*2=32$
\\
Since the DTU student has 7 liters of Ethanol and product A uses 1dl, product B 2dl and product C 1dl, we have the constraint: $x_1+2x_2+x_3\leq 70$
\\
She has 21 liters of apple juice. Product A uses 2dl, product B uses 2dl and product C uses 3dl, which gives the constraint $2x_1+2x_2+3x_3\leq 210$
\\
Lastly, she has 20 liters of Coca-Cola. Product A uses 3dl, product B uses 1dl and product C uses 1dl, which gives the constraint $3x_1+x_2+x3\leq 200$
\\
The constraints and objective function gives the following LP:
\\
\begin{equation*}
    \begin{array}{ll@{}ll}
    \text{Maximize}  & Z=6x_1+7x_2+3x_3 &\\
    \text{Subject to}& x_1+2x_2+x_3\leq 70\\
                     & 2x_1+2x_2+3x_3\leq 210\\
                     & 3x_1+x_2+x_3\leq 200\\
                     & x_1, x_2, x_3 \geq 0
\end{array}
\end{equation*}
\\
It is informed that for the optimal solution, she only makes product A and product B and that she does not use up all the apple juice.
There are 3 constraints and so there must be 3 basic variables.
Based on this information, it can be concluded that $x_1, x_2$ (product A and B) as well as the slack variable for the second constraint (apple juice) are basic variables. 
This is because $x_1$ and $x_2$ are non-zero in the solution and because the apple juice was not used up (the slack variable is also non-zero)

\vspace{5mm}
Initial system of equations:

\vspace{5mm}
\begin{tabular}{|l|l|l|l l l l l l|l|}
  \hline
  B.V           & Eq. & Z & x1 & x2 & x3 & x4 & x5 & x6 & RHS \\ \hline
  Z             & (0) & 1 & -6 & -7 & -3 & 0  & 0  & 0  & 0   \\ \hline
  x4            & (1) & 0 & 1  & 2  & 1  & 1  & 0  & 0  & 70  \\ \hline
  x5            & (2) & 0 & 2  & 2  & 3  & 0  & 1  & 0  & 210 \\ \hline
  x6            & (3) & 0 & 3  & 1  & 1  & 0  & 0  & 1  & 200 \\ \hline
\end{tabular}
\vspace{5mm}
\\
Using the fundamental insight described above, it is possible to write up the final tabeau. 
The basic variables are $x_1, x_2$ and $x_5$ and so:
\[c_B=[6, 7, 0] \ \ \ \ \ B=
\begin{bmatrix}
  1 & 2 & 0 \\
  2 & 2 & 1 \\
  3 & 1 & 0
\end{bmatrix}
\]

\pagebreak
The values are calculated in Julia like so:

\vspace{5mm}
\begin{file}[Project 1.jl]
	\begin{lstlisting}[language=matlab]
A=[1 2 1; 2 2 3; 3 1 1]
I=[1 0 0; 0 1 0; 0 0 1]
B=[1 2 0; 2 2 1; 3 1 0]
b=[70; 210; 200]
c=transpose([6,7,3])
cB=transpose([6,7,0])
   
cB*inv(B)*A-c
inv(B)*A
cB*inv(B)
inv(B)
cB*inv(B)*b
inv(B)*b    
	\end{lstlisting}
\end{file}


\vspace{5mm}
The optimal tableau becomes:

\vspace{5mm}
\begin{tabular}{|l|l|l|l l l l l l|l|}
  \hline
  B.V           & Eq. & Z & x1 & x2 & x3 & x4 & x5 & x6 & RHS \\ \hline
  Z             & (0) & 1 & 0 & 0 & 1 & 3 & 0 & 1 & 0   \\ \hline
  x1            & (1) & 0 & 1 & 0 & 0.2 & -0.2 & 0 & 0.4 & 66  \\ \hline
  x2            & (2) & 0 & 0 & 1 & 0.4 & 0.6 & 0 & -0.2 & 2 \\ \hline
  x5            & (3) & 0 & 0 & 0 & 1.8 & -0.8 & 1 & -0.4 & 74 \\ \hline
\end{tabular}


\section{Exercise 2} % Numbered section





\hrulefill 
end of the assignment
\end{document}
